\documentclass[12pt]{article}

%
%Margin - 1 inch on all sides
%
\usepackage{hyperref}
\usepackage[letterpaper]{geometry}
\usepackage{times}
\geometry{top=1.0in, bottom=1.0in, left=1.0in, right=1.0in}

%
%Doublespacing
%
\usepackage{setspace}
\singlespacing

%
%Rotating tables (e.g. sideways when too long)
%
\usepackage{rotating}

%
%Extras
%
\usepackage{siunitx}


%
%Fancy-header package to modify header/page numbering (insert last name)
%
\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{} 
\chead{} 
\rhead{Davis \thepage} 
\lfoot{} 
\cfoot{} 
\rfoot{} 
\renewcommand{\headrulewidth}{0pt} 
\renewcommand{\footrulewidth}{0pt} 
\setlength{\headheight}{14.5pt}
%To make sure we actually have header 0.5in away from top edge
%12pt is one-sixth of an inch. Subtract this from 0.5in to get headsep value
\setlength\headsep{0.333in}

%
%Bibtex and Bibliography
%
\usepackage[american]{babel}
\usepackage{csquotes}
\usepackage[style=mla,backend=biber]{biblatex}
\addbibresource{refs.bib}


%
%Begin document
%
\begin{document}
\begin{flushleft}

%%%%First page name, class, etc
Ty Davis\\
Dr. Justin Jackson\\
ECE 5110\\
April 20, 2025 \\


%%%%Title
\begin{center}
  Algorithms for Layout and Routing of VLSI Design
\end{center}



%%%%Changes paragraph indentation to 0.5in
\setlength{\parindent}{0.5in}
%%%%Begin body of paper here

\input{sections/intro}

\subsection*{Maze Routing Algorithms}

\subsubsection*{Lee's Algorithm}
\input{sections/lees}

\subsubsection*{A$^*$ Algorithm}
\input{sections/astar}

\subsubsection*{Manhattan vs Non-Manhattan Routing}
\input{sections/manhattan}

\subsubsection*{Miscellaneous Techniques}
\input{sections/misc_routing}

\subsection*{Placement and Planning}

The planning algorithms we've considered so far are
limited in their direct application to VLSI routing
and planning. Maze routing algorithms consider only
how to connect two points within a 2-dimensional space,
or a space that can otherwise be demonstrated in the
form of a graph. Such algorithms don't consider the
use of vias, other metal layers, nor do they consider
more than one path at a time.

There are more techniques within graph theory that can
be used to improve and optimize the layout of a design,
and they may have a more direct impact on the overall
VLSI design that is ultimately achieved. 

\subsubsection*{Partitioning with the Kernighan-Lin Algorithm}
\input{sections/kernighan_lin}

\subsubsection*{Rip-Up and Reroute}
\input{sections/ripup}

\subsubsection*{Simulated Annealing}
\input{sections/annealing}

\subsection*{Machine Learning}

Modern-day improvements in layout and routing are being
explored through the use of machine learning. Machine
learning is a massively expanding branch of computer science
that has proven to tackle large-scale problems like these
with lots of success. Many forms of machine learning
exist that can be used for problem solving, each with their
pros and cons.

\subsubsection*{Reinforcement Learning}
\input{sections/reinforcement}

\subsubsection*{Conclusion}
\input{sections/conclusion}


\newpage
% \nocite{*}

\printbibliography

\end{flushleft}
\end{document}
